Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2017-08-06 code/rmarkdown/article.Rmd
updates to article per reviewers suggestions

<!-- Introduction -->
\dropcap{P}rotected areas spearhead conservation efforts ([@r440]). They buffer species from anthropogenic impacts, providing places for them to persist. Since the resources available for conservation are limited, protected areas need to be sited in places that fulfill conservation objectives for minimal cost ([@r255]). To achieve this, conservation planning exercises often generate plans for entire networks of protected areas (prioritizations) to allocate resources cost-effectively and preserve broad-scale biodiversity processes ([@r9]). Intra-specific genetic variation is fundamental to long-term species persistence ([@r165; @r504]), and as a consequence, there has been increasing interest in designing prioritizations that represent this aspect of biodiversity ([@r67; @r3; @r499; @r61; @r503]).

Although the strength of natural selection is a continuous force, genetic variation is often classified as adaptive or neutral (reviewed in [@r480]). Adaptive genetic variation is associated with loci that significantly affect fitness. Typically, such "adaptive" loci are detected due to anomalous patterns among individuals (eg. [@r456; @r487]), though phenotypic-genetic associations are more likely to identify functionally important genomic regions for individual species (eg. [@r500]). By representing the full range of adaptive variation, protected areas can help ensure that populations with particularly beneficial adaptations are not lost ([@r3; @r43]). In contrast, neutral genetic variation is associated with loci that do not significantly affect fitness, but instead reflect the evolutionary history of different populations. By representing the full range of neutral variation, protected areas can safeguard against the adverse effects of low genetic diversity ([@r67]). Thus optimally sited protected area networks would aim to represent patterns of both adaptive and neutral genetic variation ([@r67; @r3; @r43]).

Recently, the use of surrogate data has been proposed to generate prioritizations that capture intra-specific genetic variation ([@r2; @r200])---without needing to utilize genetic data to achieve this. Since adaptation is ultimately driven by selection pressures, environmental variables have been proposed as surrogates for adaptive genetic variation (eg. [@r202; @r2]). Specifically, by conserving individuals in a broad range of environmental conditions, we might expect to capture individuals with a diverse set of local adaptations, and overall capture a large proportion of the adaptive genetic variation present in the species. However, the effectiveness of this approach remains unverified. Neutral genetic variation arises from a reduction in gene flow between populations. Over the last few years, the field of phylogeography has predominantly focused on describing neutral genetic diversity, and so the landscape factors that affect neutral variation are relatively well understood (reviewed in [@r501]). Potential surrogates for neutral genetic variation have been based on variables that predict the level of connectivity between different areas. For instance, according the isolation by distance model (IBD; [@r259]), populations located further apart are predicted experience less gene flow, and in turn, share fewer neutral loci. Based on this idea, spreading conservation priorities evenly across the geographic distribution of an island network has been found to capture more neutral genetic variation ([@r200]). However this remains untested in spatially contiguous systems where connectivity is complicated by many additional factors (eg. land use; [@r497])---the typical situation in most conservation planning exercises.

Here we determine whether environmental and geographic surrogates capture adaptive and neutral genetic variation respectively in the context of conservation planning. We use distribution and genomic data for 27 alpine plant species in the European Alps that was obtained by the IntraBioDiv project ([@r451]). The data was collected following a gridded sampling scheme which we adopted as planning units for this study. We show that for most species the spatial patterns of adaptive and neutral genetic variation correlated with environmental and geographic variables. We also show that for most species the level of association is strong enough to be operational for conservation planning. Finally, we demonstrate that using these surrogates results in prioritizations that secure a substantial proportion of intra-specific genetic variation.

@@

<!-- summary of methods -->
We detected putatively adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` of the 27 plant species. We used two outlier detection methods---that solely used genetic data and did not use environmental data---to identify loci under selection. These methods returned reasonably consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species assigned the same classification $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD; Table S1). Of the species that were associated with adaptive genetic variation, only a small proportion of loci were classified as being adaptive (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci showing strong signals of selection, we used non-metric multi-dimensional scaling (NMDS) analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a small number of continuous dimensions was needed to sufficiently describe their patterns of adaptive ($K = `r unique(na.omit(adaptive.k))`$ for all species; Table S2) and neutral genetic variation ($`r min(neutral.k)` \leq K \leq `r max(neutral.k)`$ for all species; Table S1). The resulting ordinations were used to construct an adaptive (if detected) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S1--S27) generally showed substantial spatial auto-correlation (eg. _Cerastium uniflorum_, Figure S34; _Dryas octopetala_, Figure S36), suggesting that the environmental and geographic variables have potential to be effective surrogates for genetic variation.

@@

<!--  introduction -->
We have shown that broad-scale environmental and geographic variables can be effective as surrogates for adaptive and neutral genetic variation in conservation planning. Our study is the first to show this using field measurements of genetic variation for a broad range of species. The spatial patterns of environmental and geographic surrogates were strongly correlated with the patterns of adaptive and neutral genetic variation for most species. Moreover, for most species, prioritizations generated using environmental and geographic targets secured a greater proportion of adaptive and neutral genetic variation than traditional conservation planning. These environmental and geographic surrogates were based on freely available data, and could be applied to any study region across the world.

<!-- surrogate/genetic held correlations -->
Our results demonstrate that environmental and geographic variables are effective surrogates for most species considered here (Figure 2). Despite this, geographic distance was a suprisingly poor surrogate for neutral genetic variation for a few species (eg. _Gypsophila repens_: $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Gypsophila_repens')$Geographic.r2CU,2)`; _Luzula alpinopilosa_: $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Luzula_alpinopilosa')$Geographic.r2CU,2)`; _Gentiana nivalis_ $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Gentiana_nivalis')$Geographic.r2CU,2)`). One explanation for this result is that geographic distance will be a poor surrogate for neutral genetic variation where spatial genetic structure is complicated by additional factors ([@r505; @r497]). For example, some species can maintain relatively high connectivity between distant populations (eg. wind dispersing plants; [@r451]), and in some places can be disrupted by landscape features (eg. anthropogenically modified land [@r497]). Overall, such species were the exception in our analysis, and both surrogates performed moderately well for most species.

@@

<!-- adaptive genetic variation secured in prioritizations-->
Our results suggest that conservation planners can secure a reasonably representative sample of the intra-specific adaptive genetic variation using only amount-based targets (Figure 2). For most species, the spatial patterns of adaptive genetic variation clustered into a few distinct groups (eg. _Carex sempervirens_ and _Cerastium uniflorum_; Figures S33 and S34 respectively). As a consequence, a prioritization would only need to select a single planning unit in each cluster to secure a representative sample. This mechanism explains why adaptive variation accumulated much more quickly than neutral genetic variation in the randomly generated prioritizations. Additionally, this mechanism also explains why the single-species prioritizations generated using only amount targets were often able to achieve high representation---they were essentially a random selection and so frequently contained planning units in different parts of the species' ranges (Figure 4a). Overall---and contrary to our original hypothesis---it seems that conventional reserve selection methods might often conserve species' adaptive genetic variation.

<!--  limitations/ weaknesses -->
There are several limitations associated with our analysis. Firstly, the size of the planning units we used (approx. 23 $\times$ 25 km) is much larger than typically used in regional conservation planning (1--10 km$^2$). We used this resolution because the genetic data were collected at this scale. Whilst we could have interpolated the genetic data to a finer resolution and used smaller planning units, this would have biased our analysis by artificially introducing additional spatial auto-correlation. Secondly, we used geographic distances as surrogates for neutral genetic variation, yet distances that incorporate data on topography may better describe connectivity in the study area. However, such distances often require species-specific scaling (eg. [@r497]), and so cannot easily be utilized in multi-species planning exercises. Thirdly, we used amplified fragment length polymorphism data (AFLP; [@r453]) to describe genetic variation. Whilst next-generation sequencing provides higher resolution genetic information than AFLP data ([@r480]), we know of no suitable multi-species genomic data set, and our methodology would still have utilized only the main gradients of the genetic variation to generate prioritizations in a feasible period of time. Furthermore, even with modern population genomic approaches, a survey can at best hope to identify markers that are linked to functionally adaptive variants.

<!--  conclusion -->
Broad-scale environmental and geographic variables are generally effective surrogates for representing adaptive and neutral genetic variation for most species in our study system. Moreover, data to calculate the surrogate variables are freely available for any location in the world. Careful use of such surrogates in conservation planning could vastly improve the chances of long-term biodiversity persistence for relatively little additional cost.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r451]; Figure 3a). All data, code, and results are stored in an online repository to permit replication and validation of this study (\url{www.github.com/jeffreyhanson/genetic-surrogates}). This data set has been used to explore patterns of adaptive (eg. [@r455]) and neutral genetic variation (eg. [@r478]), and the potential for species richness as a surrogate for genetic diversity ([@r486]). Data were collected using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 $\times$ 25 km; Figure S31). Project surveyors visited every second grid cell, and for each species, they collected samples from three individuals if any individuals were found. They genotyped samples using AFLPs, and constructed matrices denoting the presence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478], Table 1). Thus the data set contains information describing the genomic properties of individuals for each species over a geographic grid. We used these data because they comprised comparable genetic information for a range of species with different evolutionary and life histories collected using a standardized sampling scheme.

@@

# plot species richness
p1 <- ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70') +
  geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat,
    group=group, fill=Species_richness), color=NA) +
  scale_fill_gradientn(name='Richness',
    colors=brewer.pal(5, 'YlGn'),
    guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
  ) +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
    panel.border=element_rect(color='black', fill=NA, size=1)
  ) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  ) + geom_text(aes_string(x='long',y='lat'), data=panel.DF, label='(a)')

qn01 <- scales::rescale(quantile(grid.PLY@data$pop.density, seq(0,1,length.out=9), na.rm=TRUE))
p2 <- ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70') +
  geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat,
    group=group, fill=pop.density), color=NA) +
  scale_fill_gradientn(name='Cost',
    colors=brewer.pal(5,'YlOrRd'),
    values=qn01,
    guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
  ) +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
    panel.border=element_rect(color='black', fill=NA, size=1)
  ) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  )  + geom_text(aes_string(x='long',y='lat'), data=panel.DF, label='(b)')

@@

We created environmental and geographic surrogate variables for each species (Figure S32). To describe the geographic location of each planning unit (Figure S33), we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit (Figure S34), we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subjected the climatic values associated with the planning units they were found in to a principal components analysis (PCA; Table S1). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterize climatic variation found across the species' geographic distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more comparable environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these environmental or geographic spaces.

@@

The first outlier detection method involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} (version 2.1; [@r456]). We adopted a similar methodology to Bothwell _et al._ ([-@r455]) and applied it to each of the species separately. Following their methodology, we initially grouped conspecifics into genetic lineages to further minimize false-positives (Figures S36--S62), by fitting admixture and correlated alleles models implemented in \texttt{Structure} (version 2.3.4; [@r462]; `r structure.params.LST[[MODE]]$numruns` replicates per species; `r format(structure.params.LST[[MODE]]$admburnin, big.mark=',', scientific=FALSE)` admixture burnin iterations; `r format(structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` burnin iterations; `r format(structure.params.LST[[MODE]]$numreps+structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` total iterations) using the number of lineages previously determined by Alvarez _et al._ ([@r478]) and combining replicate runs using \texttt{ClumPP} (version 1.1.2; [@r459]; greedy algorithm based on the $G^{\prime}$ statistic; `r format(clumpp.params.LST[[MODE]]$repeats, big.mark=',', scientific=FALSE)` iterations). We then ran $\texttt{Bayescan}$ for each species using these lineages (1:1 prior odds; `r bayescan.params.LST[[MODE]]$reps` replicates per species; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r format(bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` burn-in iterations; `r format(bayescan.params.LST[[MODE]]$n+bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` total iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations) using a suitable false discovery rate ($q \leq `r bayescan.params.LST[[MODE]]$fdr`$; [@r466]). We omitted individuals if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$).

The second outlier detection method involved fitting PCAs to identify outlier loci (implemented in the \texttt{pcadapt R} package; [@r487]). To enable comparisons between the two outlier detection methods, we used the same individuals in this analysis as in the \texttt{BayeScan} analysis. For each of the 27 species, we first imputed missing data by replacing missing values with the average frequency among conspecifics, then ran a PCA over the loci matrix, and extracted the minimum number of components needed to secure the over-arching population level variation among the loci (`r pcadapt.params.LST[[MODE]]$min.variance.explained*100` % of the variation in loci). We then computed _q_-values using Mahalanobis distances, and used the same false discovery rate used in the \texttt{BayeScan} analysis to identify loci under selection (using the \texttt{qvalue R} package; [@r491]).

>>>>

<!-- Introduction -->
\dropcap{P}rotected areas spearhead conservation efforts ([@r507]). They buffer species from anthropogenic impacts, providing places for them to persist. Since the resources available for conservation are limited, protected areas need to be sited in places that fulfill conservation objectives for minimal cost ([@r255]). To achieve this, conservation planning exercises often generate plans for entire networks of protected areas (prioritizations) to allocate resources cost-effectively and preserve broad-scale biodiversity processes ([@r9]). Intra-specific genetic variation is fundamental to long-term species persistence ([@r165; @r504]), and as a consequence, there has been increasing interest in designing prioritizations that represent this aspect of biodiversity ([@r67; @r3; @r499; @r61; @r503]).

Although the strength of natural selection is a continuous force, genetic variation is often classified as adaptive or neutral (reviewed in [@r480]). Adaptive genetic variation is associated with loci that significantly affect fitness. Typically, such "adaptive" loci are detected due to anomalous patterns among individuals (e.g. [@r456; @r487]), though phenotypic-genetic associations are more likely to identify functionally important genomic regions for individual species (e.g. [@r500]). By representing the full range of adaptive variation, protected areas can fortify a species' capacity to persist in a range of different conditions ([@r3; @r43]). In contrast, neutral genetic variation is associated with loci that do not significantly affect fitness, but instead reflect the evolutionary history of different populations. By representing the full range of neutral variation, protected areas can safeguard against the adverse effects of low genetic diversity ([@r67]). Thus optimally sited protected area networks would aim to represent patterns of both adaptive and neutral genetic variation ([@r67; @r3; @r43]).

Recently, the use of surrogate data has been proposed to generate prioritizations that capture intra-specific genetic variation ([@r2; @r506; @r200])---without needing to utilize genetic data to achieve this. Since adaptation is ultimately driven by selection pressures, environmental variables have been proposed as surrogates for adaptive genetic variation (e.g. [@r202; @r2]). Specifically, by conserving individuals in a broad range of environmental conditions, we might expect to capture individuals with a diverse set of local adaptations, and overall capture a large proportion of the adaptive genetic variation present in the species. However, the effectiveness of this approach remains unverified. Neutral genetic variation arises from a reduction in gene flow between populations. Over the last few years, the field of phylogeography has predominantly focused on describing neutral genetic diversity, and so the landscape factors that affect neutral variation are relatively well understood (reviewed in [@r501]). Potential surrogates for neutral genetic variation have been based on variables that predict the level of connectivity between different areas. For instance, according the isolation by distance model (IBD; [@r259]), populations located further apart are predicted to experience less gene flow, and in turn, share fewer neutral loci. Based on this idea, spreading conservation priorities evenly across the geographic distribution of an island network has been found to capture more neutral genetic variation ([@r200]). However this remains untested in spatially contiguous systems where connectivity is complicated by many additional factors (e.g. land use; [@r497])---the typical situation in most conservation planning exercises.

Here we determine whether environmental and geographic surrogates capture adaptive and neutral genetic variation respectively in the context of conservation planning. We use distribution and genomic data for 27 alpine plant species in the European Alps that was obtained by the IntraBioDiv project ([@r451]). The data were collected following a gridded sampling scheme which we adopted as planning units for this study. We show that for most species the spatial patterns of adaptive and neutral genetic variation correlated with environmental (obtained from WorldClim; [@r33]) and geographic variables. We also show that for most species the level of association is strong enough to be operational for conservation planning. Finally, we demonstrate that using these surrogates results in prioritizations that secure a substantial proportion of intra-specific genetic variation.

@@

<!-- summary of methods -->
We detected putatively adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` of the 27 plant species. We used two outlier detection methods---that solely used genetic data and did not use environmental data---to identify loci under selection. These methods returned reasonably consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species assigned the same classification $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD; Table S1). Of the species that were associated with adaptive genetic variation, only a small proportion of loci were classified as being adaptive (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci showing strong signals of selection, we used non-metric multi-dimensional scaling (NMDS) analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a small number of continuous dimensions was needed to sufficiently describe their patterns of adaptive ($K = `r unique(na.omit(adaptive.k))`$ for all species; Table S2) and neutral genetic variation ($`r min(neutral.k)` \leq K \leq `r max(neutral.k)`$ for all species; Table S1). The resulting ordinations were used to construct an adaptive (if detected) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S1--S27) generally showed substantial spatial auto-correlation (e.g. _Cerastium uniflorum_, Figure S34; _Dryas octopetala_, Figure S36), suggesting that the environmental and geographic variables have potential to be effective surrogates for genetic variation.

@@

<!--  introduction -->
We have shown that broad-scale environmental and geographic variables can be effective as surrogates for adaptive and neutral genetic variation in conservation planning. Our study is the first to show this using field measurements of genetic variation for a broad range of plant species. The spatial patterns of environmental and geographic surrogates were strongly correlated with the patterns of adaptive and neutral genetic variation for most species. Moreover, for most species, prioritizations generated using environmental and geographic targets secured a greater proportion of adaptive and neutral genetic variation than traditional conservation planning. These environmental and geographic surrogates were based on freely available global data sets and, with exception to a few places with poor estimates ([@r33]), could be applied to any study region across the world.

<!-- surrogate/genetic held correlations -->
Our results demonstrate that environmental and geographic variables are effective surrogates for most species considered here (Figure 2). Despite this, geographic distance was a suprisingly poor surrogate for neutral genetic variation for a few species (e.g. _Gypsophila repens_: $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Gypsophila_repens')$Geographic.r2CU,2)`; _Luzula alpinopilosa_: $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Luzula_alpinopilosa')$Geographic.r2CU,2)`; _Gentiana nivalis_ $R^2$ = `r round(filter(surrogate.spp.DF, Species=='Gentiana_nivalis')$Geographic.r2CU,2)`). One explanation for this result is that geographic distance will be a poor surrogate for neutral genetic variation where spatial genetic structure is complicated by additional factors ([@r505; @r497]). For example, some species can maintain relatively high connectivity between distant populations (e.g. wind dispersing plants; [@r451]), and in some places can be disrupted by landscape features (e.g. anthropogenically modified land; [@r497]). Overall, such species were the exception in our analysis, and both surrogates performed moderately well for most species.

@@

<!-- adaptive genetic variation secured in prioritizations-->
Our results suggest that conservation planners can secure a representative sample of the intra-specific adaptive genetic variation using only amount-based targets (Figure 2). This result was evident in both the single- and multi-species prioritizations. One explanation for the single-species prioritizations is that because the spatial patterns of adaptive variation tended to cluster into a few groups (e.g. _Carex sempervirens_ and _Cerastium uniflorum_; Figures S33 and S34), a random selection of planning units across a species' distribution would have had a fairly high chance of capturing planning units that contained individuals belonging to multiple clusers. This mechanism also explains why adaptive variation accumulated much more quickly than neutral genetic variation in the randomly generated prioritizations (Figure 1). On the other hand, one potential explanation for the multi-species prioritization is that because it was generated using a comprehensive set of species---each with their own habitat preferences---the solution was forced to secure each species in a range of different suitable habitats and, in turn, capture a representative sample of the species' adaptive genetic variation. This would also suggest that these surrogates may be robust to missing distribution data when prioritizations are generated using a comprehensive set of species. Overall---and contrary to our original hypothesis---it seems that conventional reserve selection methods might often conserve species' adaptive genetic variation.

<!--  limitations/ weaknesses -->
There are several limitations associated with our analysis. Firstly, the size of the planning units we used (approx. 23 $\times$ 25 km) is much larger than typically used in regional conservation planning (1--10 km$^2$). We used this resolution because the genetic data were collected at this scale. Whilst we could have interpolated the genetic data to a finer resolution, this would have introduced additional spatial auto-correlation and biased our analysis. Secondly, we used geographic distances as surrogates for neutral genetic variation. Although distances that incorporate data on dispersal cost may perform better (e.g. topograpgy), such distances often require species-specific scaling (e.g. [@r497]) and so cannot easily be utilized in multi-species planning exercises. Thirdly, we used amplified fragment length polymorphism data (AFLP; [@r453]) to describe genetic variation. Whilst next-generation sequencing provides higher resolution genetic information ([@r480]), we know of no suitable multi-species genomic data set and our methodology would still have utilized only the main gradients of the genetic variation to generate prioritizations in a feasible period of time. Furthermore, even with modern population genomic approaches, a survey can at best hope to identify markers that are linked to functionally adaptive variants. Fourthly, none of the species we investigated here are known to be at serious risk of extinction (IUCN Red List of Threatened Species 2017). Although many conservation priorities seek to preserve broad-scale patterns of biodiversity ([@r255]), future work should aim to establish if these surrogates are effective for endangered species.

<!--  conclusion -->
Broad-scale environmental and geographic variables are generally effective surrogates for representing adaptive and neutral genetic variation for most species in our study system. Although genetic data are still desperately needed to guide conservation efforts for species at serious risk of extinction, careful use of such surrogates in conservation planning could vastly improve the chances of long-term biodiversity persistence for relatively little additional cost.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r451]; Figure 3a). All data, code, and results are stored in an online repository to permit replication and validation of this study (\url{www.github.com/jeffreyhanson/genetic-surrogates}). This data set has been used to explore patterns of adaptive (e.g. [@r455]) and neutral genetic variation (e.g. [@r478]), and the potential for species richness as a surrogate for genetic diversity ([@r486]). Data were collected using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 $\times$ 25 km; Figure S31). Project surveyors visited every second grid cell, and for each species, they collected samples from three individuals if any individuals were found. They genotyped samples using AFLPs, and constructed matrices denoting the presence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478], Table 1). Thus the data set contains information describing the genomic properties of individuals for each species over a geographic grid. We used these data because they comprised comparable genetic information for a range of species with different evolutionary and life histories collected using a standardized sampling scheme.

@@

# plot species richness
p1 <- ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70', size=0.01) +
  geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat,
    group=group, fill=Species_richness), color=NA) +
  scale_fill_gradientn(name='Richness',
    colors=brewer.pal(5, 'YlGn'),
    guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
  ) +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
    panel.border=element_rect(color='black', fill=NA, size=1)
  ) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  ) + geom_text(aes_string(x='long',y='lat'), data=panel.DF, label='(a)')

qn01 <- scales::rescale(quantile(grid.PLY@data$pop.density, seq(0,1,length.out=9), na.rm=TRUE))
p2 <- ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70', size=0.01) +
  geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat,
    group=group, fill=pop.density), color=NA) +
  scale_fill_gradientn(name='Cost',
    colors=brewer.pal(5,'YlOrRd'),
    values=qn01,
    guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
  ) +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
    panel.border=element_rect(color='black', fill=NA, size=1)
  ) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  )  + geom_text(aes_string(x='long',y='lat'), data=panel.DF, label='(b)')

@@

We created environmental and geographic surrogate variables for each species (Figure S32). To describe the geographic location of each planning unit (Figure S33), we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit (Figure S34), we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; obtained from WorldClim; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subjected the climatic values associated with the planning units they were found in to a principal components analysis (PCA; Table S1). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterize climatic variation found across the species' geographic distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more comparable environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these environmental or geographic spaces.

@@

The first outlier detection method involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} (version 2.1; [@r456]). We adopted a similar methodology to Bothwell _et al._ ([-@r455]) and applied it to each of the species separately. Following their methodology, we initially grouped conspecifics into genetic lineages to further minimize false-positives (Figures S36--S62), by fitting admixture and correlated alleles models implemented in \texttt{Structure} (version 2.3.4; [@r462]; `r structure.params.LST[[MODE]]$numruns` replicates per species; `r format(structure.params.LST[[MODE]]$admburnin, big.mark=',', scientific=FALSE)` admixture burnin iterations; `r format(structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` burnin iterations; `r format(structure.params.LST[[MODE]]$numreps+structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` total iterations) using the number of lineages previously determined by Alvarez _et al._ ([@r478]) and combining replicate runs using \texttt{ClumPP} (version 1.1.2; [@r459]; greedy algorithm based on the $G^{\prime}$ statistic; `r format(clumpp.params.LST[[MODE]]$repeats, big.mark=',', scientific=FALSE)` iterations). We then ran $\texttt{BayeScan}$ for each species using these lineages (1:1 prior odds; `r bayescan.params.LST[[MODE]]$reps` replicates per species; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r format(bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` burn-in iterations; `r format(bayescan.params.LST[[MODE]]$n+bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` total iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations) using a suitable false discovery rate ($q \leq `r bayescan.params.LST[[MODE]]$fdr`$; [@r466]). We omitted individuals if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$).

The second outlier detection method involved fitting PCAs to identify outlier loci (implemented in the \texttt{pcadapt R} package; [@r496]). To enable comparisons between the two outlier detection methods, we used the same individuals in this analysis as in the \texttt{BayeScan} analysis. For each of the 27 species, we first imputed missing data by replacing missing values with the average frequency among conspecifics, then ran a PCA over the loci matrix, and extracted the minimum number of components needed to secure the over-arching population level variation among the loci (`r pcadapt.params.LST[[MODE]]$min.variance.explained*100` % of the variation in loci). We then computed _q_-values using Mahalanobis distances, and used the same false discovery rate used in the \texttt{BayeScan} analysis to identify loci under selection (using the \texttt{qvalue R} package; [@r491]).
